Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-12 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
F15 Description

\subsection{$F_{15}:\frac{D}{m}$-group Shifted and $m$-rotated Rastrigins Function}
The most common use of JavaScript is in the development of
asynchronous Web applications. Scripts are embedded in HTML pages and change
the state of with the Document Object Model (DOM) of the page, by sending or
retrieveing data asynchronously from a server. For these purpose JavaScript has
been traditionally implemented as an interpreted language not designed for the
development of high performance systems. Current JavaScript virtual machines (VMs)
are closing the gap, for instance the Google V8 is an engine specifically designed
for fast execution of large JavaScript applications. Also V8 compiles JavaScript
source code directly into machine code when it is first executed. 
There are no intermediate byte codes or interpreter.
[\url{ https://developers.google.com/v8/design#mach_code}].
JavaScript has gained popularity in server-side development using runtime
environments such as Node.js and is also used in desktop and mobile applications.
To further evaluate how a current JavaScript implemantation can be used by a
computer scientist for the development of complex optimization problems,
a benchmark function, which was provided by CEC2010 Special Session on
Large-Scale Global Optimization [], is used in this section.

\begin{equation}
F_{rastrigin}(x)=\sum\limits_{i=1}^\frac{D} [x_{i}^{2}-10\cos(2\pi x_i)+10  ] 
\end{equation}

\begin{equation}
F_{rot_rastrigin}(x)=F_{rastrigin}(\textbf{z}), \textbf{z}= \textbf{x} * \textbf{M}
\end{equation}

\begin{equation}
F_{15}(x)=\sum\limits_{k=1}^\frac{D}{m}F_{rot_rastrigin}[\textbf{z}(F_{(k-1)*m+1}:P_{k*m})] 
\end{equation}

%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

>>>>

\subsection{$F_{15}:\frac{D}{m}$-group Shifted and $m$-rotated Rastrigins Function}
The most common use of JavaScript is in the development of
asynchronous Web applications. Scripts are embedded in HTML pages and change
the state of with the Document Object Model (DOM) of the page, by sending or
retrieveing data asynchronously from a server. For these purpose JavaScript has
been traditionally implemented as an interpreted language not designed for the
development of high performance systems. Current JavaScript virtual machines (VMs)
are closing the gap, for instance the Google V8 is an engine specifically designed
for fast execution of large JavaScript applications. Also V8 compiles JavaScript
source code directly into machine code when it is first executed. 
There are no intermediate byte codes or interpreter.
[\url{ https://developers.google.com/v8/design#mach_code}].
JavaScript has gained popularity in server-side development using runtime
environments such as Node.js and is also used in desktop and mobile applications.
To further evaluate how a current JavaScript implemantation can be used by a
computer scientist for the development of complex optimization problems,
a benchmark function, which was provided by CEC2010 Special Session on
Large-Scale Global Optimization [] as Function 15 is used in this section. 
The function is described next.

The basic Rastrigins function is separable[], and is defined as follows;
\begin{equation}
F_{rastrigin}(x)=\sum\limits_{i=1}^\frac{D} [x_{i}^{2}-10\cos(2\pi x_i)+10  ] 
\end{equation}
where $D$ is the dimension and $x = (x1, x2, · · · , x_{D})$ is a
$D$-dimensional row vector (i.e., a $1 × D$ matrix). Rastrigin’s function 
is a classical multimodal problem. It is difficult since the number of local
optima grows exponentially with the increase of dimensionality. To make it 
nonseparable, an orthogonal matrix is also used for coordinate rotation.
The rotated Rastrgin’s function is defined as follows:
\begin{equation}
F_{rot_rastrigin}(x)=F_{rastrigin}(\textbf{z}), \textbf{z}= \textbf{x} * \textbf{M}
\end{equation}
Where \textbf{M}_{is} a $D×D$ orthogonal matrix.

The benchmark  emulates real-world optimization problems that most likely will consist 
of different groups of parameters with strong dependencies within
but little interaction between the groups. This issue is reflected in the benchmark
problems by first randomly dividing the objective variables
into several groups, each of which contains a number of variables. The parameter $m$ 
is used to control the number of variables in each group and hence, defining the degree
of separability:
\begin{equation}
F_{15}(x)=\sum\limits_{k=1}^\frac{D}{m}F_{rot_rastrigin}[\textbf{z}(F_{(k-1)*m+1}:P_{k*m})] 
\end{equation}
For the benchmark $D = 1000$, Group size $m = 50$, $\textbf{x} = (x_1, x_2, · · · , x_{D})$ is the
candidate solution, $\textbf{o} = (o_1, o_2, · · · , o_{D})$ is the shifted global optimum,
$\textbf{z} = \textbf{x} − \textbf{o}$ is the shifted candidate solution and
finally $\textbf{P}$ is a random permutation of ${1, 2, · · · ,D}$.
%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
